### 2021-02-19 architecture.tex
Add a complete description of the GCN

For each symbol in the problem,
we seek to find a vector representation, i.e., an \emph{embedding},
that captures the symbol's properties that are relevant
for the correctly ranking the symbol in the observed symbol precedences.
The symbol embeddings are modeled\todo{MS: embeddings are ``output''? } by a \gls{rgcn} \cite{Schlichtkrull2017},
\todo{Can I use the term \gls{rgcn} when I use a modified version? Namely, the activation is called earlier. MS: sounds good.}
which is a stack of graph convolutional layers.
Each layer consists of a collection of differentiable modules --- one for each edge type.
A pass through the convolutional layer takes the embeddings of all symbols,
converts them by the edge modules of the adjacent edges to form the messages,\todo{MS: ``message'' occurs for the first time. 
Maybe ``a message'', or explain beforehand.}
passes the messages to the destination nodes
and aggregates the incoming messages of each node.
In the simple case that each edge module is a dense layer,\todo{MS: hnidopich nevi, co to znamena ``dense layer''}
the output embedding $h^{(l+1)}$ is computed from the input embeddings $h^{(l)}$ in the following manner:
$$
h_i^{(l+1)} =
\sum_{r \in \mathcal{R}} \sigma \Parentheses{\sum_{j \in \mathcal{N}_i^r} \frac{1}{c_{ji}} h_j^{(l)} W_r^{(l)}}
$$
%$$
%h_i^{(l+1)} =
%\mathrm{LayerNorm} \Parentheses{h_i^{(l)} + \sum_{r \in \mathcal{R}} \sigma \Parentheses{\sum_{j \in %\mathcal{N}_i^r} \frac{1}{c_{ji}} h_j^{(l)} W_r^{(l)}}}
%$$
% Inspiration: https://ufal.mff.cuni.cz/~straka/courses/npfl114/1920/slides.pdf/npfl114-07.pdf - slide 27 - Transformer
\todo{FB: Mention inspiration: Transformer. See Straka's slides.}
$h_i^{(l)}$ denotes the embedding of node $i$ at layer $l$.
$\mathcal{R}$ denotes the set of all relations in the graph.
$\sigma$ denotes the activation function, for example the \gls{relu}.
$\mathcal{N}_i^r$ denotes the set of neighbors of node $i$ under relation $r$.
$c_{j, i, r} = \sqrt{\card{\mathcal{N}_j^r}} \sqrt{\card{\mathcal{N}_i^r}}$ is a normalization constant \cite{kipf2017semisupervised}.
$W_r^{(l)}$ is a trainable weight matrix representing relation $r$ at layer $l$.

>>>>

For each symbol in the problem,
we seek to find a vector representation, i.e., an \emph{embedding},
that captures the symbol's properties that are relevant
for the correctly ranking the symbol in the observed symbol precedences.
The symbol embeddings are modeled\todo{MS: embeddings are ``output''? } by a \gls{rgcn} \cite{Schlichtkrull2017},
\todo{Can I use the term \gls{rgcn} when I use a modified version? Namely, the activation is called earlier. MS: sounds good.}
which is a stack of graph convolutional layers.
Each layer consists of a collection of differentiable modules---one module per edge type.
The computation of the \gls{gcn} starts with assigning each node an initial embedding
and then repeatedly updates the embeddings by passing them through convolutional layers.
\todo{Ensure terms are clear (preferably defined): embedding, vector, trainable vector, feature vector.}

The initial embedding is a concatenation of two vectors:
a node feature vector (typically empty)
and a trainable vector shared by all nodes of the same type.
In our particular implementation,
feature vectors are used in nodes that correspond to clauses and symbols.
Each clause node has a feature vector with a one-hot encoding of the role of the clause,
which can be either axiom, assumption, or negated conjecture.
Each symbol node has a feature vector with two bits of data:
whether the symbol was introduced into the problem during preprocessing,
and whether the symbol appears in a conjecture clause.

One pass through the convolutional layer
updates the node embeddings by passing a message along each of the edges.
\todo{MS: ``message'' occurs for the first time. 
Maybe ``a message'', or explain beforehand.}
For an edge of type $r \in \mathcal{R}$ going from source node $s$ to destination node $d$ at layer $l$,
the message is composed by converting the embedding of the source node $h_s^{(l)}$
using the module associated with the edge type $r$.
In the simple case that the module is a dense layer with weights $W_r^{(l)}$,
\todo{MS: hnidopich nevi, co to znamena ``dense layer''}
the message is $h_s^{(l)} W_r^{(l)}$.
Each message is then divided by a normalization constant
$c_{s,d} = \sqrt{\card{\mathcal{N}_s^r}} \sqrt{\card{\mathcal{N}_d^r}}$ \cite{kipf2017semisupervised},
where $\mathcal{N}_n^r$ is the set of neighbors of node $n$ under the relation $r$.
\todo{FB: Mention that we mean both in- and out-neighbors?}
Once all the messages are computed,
they are aggregated by the destination nodes to form the new node embedding.
Each node $d$ aggregates all the incoming messages of a given edge type $r$ by summation,
then passes the sum through an activation function $\sigma$ such as the \gls{relu},
and finally aggregates the messages across the edge types by summation,
yielding the new embedding $h_d^{(l+1)}$.
The following formula captures the update of embedding of node $d$:
$$
h_d^{(l+1)} =
\sum_{r \in \mathcal{R}} \sigma \Parentheses{\sum_{j \in \mathcal{N}_s^r} \frac{1}{c_{s,d}} h_s^{(l)} W_r^{(l)}}
$$
%$$
%h_i^{(l+1)} =
%\mathrm{LayerNorm} \Parentheses{h_i^{(l)} + \sum_{r \in \mathcal{R}} \sigma \Parentheses{\sum_{j \in %\mathcal{N}_i^r} \frac{1}{c_{ji}} h_j^{(l)} W_r^{(l)}}}
%$$
% Inspiration: https://ufal.mff.cuni.cz/~straka/courses/npfl114/1920/slides.pdf/npfl114-07.pdf - slide 27 - Transformer
%\todo{FB: Mention inspiration: Transformer. See Straka's slides.}
